---
title: "Linkedin Network"
output: html_document
---

As part of the assignment, we decided to analyze our "Linkedin" network.

Each vertex in the graph represents a Linkedin user, and each edge represents connection between the two users in the Linkedin network.

This is the initial Graph:

```{r message=FALSE, warning=FALSE}
library(igraph)
linkedinGraph <- read.graph(file = "LinkedinGraph.gml",format = "gml")
linkedinGraph$layout <- layout.fruchterman.reingold(linkedinGraph) 
plot(linkedinGraph,vertex.size=5,vertex.label.cex =0.7,asp=FALSE)
```

We computed the centrality attributes of each vertex by the following lines:

```{r}
V(linkedinGraph)$Betweeness = betweenness(linkedinGraph)
V(linkedinGraph)$Closeness = closeness(linkedinGraph)
V(linkedinGraph)$EigenVector = evcent(linkedinGraph)$vector
```

We found the vertex with the best centrality attributes by the following lines:
```{r}
V(linkedinGraph)$label[which(V(linkedinGraph)$Betweeness == max(betweenness(linkedinGraph)))]
V(linkedinGraph)$label[which(V(linkedinGraph)$Closeness == max(closeness(linkedinGraph)))]
V(linkedinGraph)$label[which(V(linkedinGraph)$EigenVector == max(evcent(linkedinGraph)$vector))]
```

Bar Haim and Dana Kedem are HR recruiters that are connected to most of my Linkedin connections, therefore they have the best centrality attributes.

### Grivan-Newman algorithm

We decided to analyze once again the graph with Grivan-Newman algorithm, we used the following code lines:

```{r}
linkedinGraph = simplify(linkedinGraph)

#girvan-newman
ebc <- edge.betweenness.community(linkedinGraph, directed=F)

# color the nodes according to their membership
mods <- sapply(0:ecount(linkedinGraph), function(i){
  g2 <- delete.edges(linkedinGraph, ebc$removed.edges[seq(length=i)])
  cl <- clusters(g2)$membership
  modularity(linkedinGraph,cl)
})
g2<-delete.edges(linkedinGraph, ebc$removed.edges[seq(length=which.max(mods)-1)])
V(linkedinGraph)$color=clusters(g2)$membership

# layout for the graph
linkedinGraph$layout <- layout.fruchterman.reingold
plot(linkedinGraph,vertex.size=5,vertex.label.cex =0.7,asp=FALSE)
```

We can see that we have 3 major communities:

1. Blue - University friends and HR recruiters.
2. Green - Work Colleagues.
3. Yellow - Friends from Previous University.

To summarize we got 17 communities(there are a lot of communities also because the isolated vertexes) with modularity of 0.1856942.

### Walk Trap

The second algorithm we used to analyze the network is Walk Trap.
Here we can see the code:
```{r}
wtc <- walktrap.community(linkedinGraph)
memb <- cutat(wtc, steps= which.max(wtc$modularity)-1)
plot(linkedinGraph, layout=layout.fruchterman.reingold, vertex.size=5, vertex.color=memb, asp=FALSE)
```

Within this graph we see 4 major communities:
1. Blue - Friends from Previous University.
2. Orange - Work Colleagues.
3. Green - HR recruiters.
4. Yellow - University friends.

From our point of view, it's looks like the walk-trap algorithm succeed better than the girvan-newman algorithm, and the communities  diversity is more accurate.

With the walk-trap algorithm we got 11 communities(including the isolated nodes).

We got the following modularity value:
```{r}
modularity(wtc)
```